*Platynereis dumerilii* three-day-old connectome --- cell-type compendium

### 2025-07-07 supplements/celltype_compendium_website/index.qmd
add celltyp ecompendium website and morphological renderings of brain, girdle, MB

---
title: "*Platynereis dumerilii* three-day-old connectome --- cell-type compendium"
format:
  html:
    toc: true
    toc-depth: 3
    toc-expand: 3
---

```{r}
#| echo: false
#| include: FALSE
library(dplyr)
library(rio)
library(tinytable)
library(knitr)
library(gt)
library(catmaid)
library(rgl)
library(htmltools)

# catmaid connection, needs username, password AND token - weird!
{
  # can run this separate file using source function
  conn <- source("~/R/conn.R")
  #for larger calls we need to use http/1, see https://www.gitmemory.com/issue/natverse/rcatmaid/158/641537466
  #for this we configure to http/1.1
  conn_http1 = catmaid_login(conn=conn, config=httr::config(ssl_verifypeer=0, http_version=1))
}

```

# Neuronal cell types

## Sensory neurons

```{r}
#| echo: false

celltypes <- rio::import("../Supplementary_Table1.csv")

#functions for table and neuron plot
plot_cell_name <- function(annotation, type_of_cell){
  name <- celltypes |>
  filter(`Sensory/inter/motor neuron` == type_of_cell) |> 
  filter(`CATMAID annotation` == annotation) |> 
  pull(`CATMAID annotation`, `name of cell type`)

kable(name, col.names = c("name of cell type", "CATMAID annotation"))
}

plot_cell_chars <- function(annotation, type_of_cell){
  celltypes |>
  filter(`Sensory/inter/motor neuron` == type_of_cell) |>
  filter(`CATMAID annotation` == annotation) |>   
  select(`number of cells`, `soma position`, `region`, `transmitter phenotype`, `postsynaptic partners (<10 synapses)`, `presynaptic partners (<10 synapses)`, `reference`) |>
  kable()
}

```

### Photoreceptors

#### Rhabdomeric photoreceptors

```{r}
#| echo: false
# PRC
annot <- "celltype1"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```
![](snapshots/celltype1.png){height=200}

[3D visualisation](celltype_RGLs/celltype1.html){target="_blank"}

```{r}
#| echo: false

# eyespot-PRCR3
annot <- "celltype33"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype33.png){height=200}

[3D visualisation](celltype_RGLs/celltype33.html){target="_blank"}

```{r}
#| echo: false

# eyespot-PRCR1
annot <- "celltype34"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype34.png){height=200}

[3D visualisation](celltype_RGLs/celltype34.html){target="_blank"}

#### Ciliary photoreceptors {#sec-cPRC}

```{r}
#| echo: false

# cPRC
annot <- "celltype5"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype5.png){height=200}

[3D visualisation](celltype_RGLs/celltype5.html){target="_blank"}

### Mechanoreceptors

#### CR (collar receptor) hydrodynamic vibration-receptor neurons

```{r}
#| echo: false

# hCR
annot <- "celltype100"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype100.png){height=200}

[3D visualisation](celltype_RGLs/celltype100.html){target="_blank"}

```{r}
#| echo: false

# ventralpygCR
annot <- "celltype101"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype101.png){height=200}

[3D visualisation](celltype_RGLs/celltype101.html){target="_blank"}

```{r}
#| echo: false

# doCRunp
annot <- "celltype102"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype102.png){height=200}

[3D visualisation](celltype_RGLs/celltype102.html){target="_blank"}

#### PU (penetrating uniciliated) mechanosensory neurons

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype88")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype88.png){height=200}

[3D visualisation](celltype_RGLs/celltype88.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype89")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype89.png){height=200}

[3D visualisation](celltype_RGLs/celltype89.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
#VentraltrunkPUunp
annot <- ("celltype90")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype90.png){height=200}

[3D visualisation](celltype_RGLs/celltype90.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype91")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype91.png){height=200}

[3D visualisation](celltype_RGLs/celltype91.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
#hPUc1
annot <- ("celltype92")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype92.png){height=200}

[3D visualisation](celltype_RGLs/celltype92.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype93")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype93.png){height=200}

[3D visualisation](celltype_RGLs/celltype93.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype94")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype94.png){height=200}

[3D visualisation](celltype_RGLs/celltype94.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype95")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype95.png){height=200}

[3D visualisation](celltype_RGLs/celltype95.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype96")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype96.png){height=200}

[3D visualisation](celltype_RGLs/celltype96.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype97")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype97.png){height=200}

[3D visualisation](celltype_RGLs/celltype97.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype88-98
annot <- ("celltype98")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype98.png){height=200}

[3D visualisation](celltype_RGLs/celltype98.html){target="_blank"}

#### PB (penetrating biciliated) mechanosensory neurons  {#sec-PB}

```{r}
#| echo: false

# PB neurons celltype80 and 54
annot <- ("celltype80")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype80.png){height=200}

[3D visualisation](celltype_RGLs/celltype80.html){target="_blank"}

```{r}
#| echo: false

# PB neurons celltype80 and 54
#pygPBunp
annot <- ("celltype54")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype54.png){height=200}

[3D visualisation](celltype_RGLs/celltype54.html){target="_blank"}

#### Flow-sensory MS neurons

```{r}
#| echo: false

# MS neurons celltype35-38
annot <- ("celltype35")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype35.png){height=200}

[3D visualisation](celltype_RGLs/celltype35.html){target="_blank"}

```{r}
#| echo: false

# MS neurons celltype35-38
annot <- ("celltype36")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype36.png){height=200}

[3D visualisation](celltype_RGLs/celltype36.html){target="_blank"}

```{r}
#| echo: false

# MS neurons celltype35-38
annot <- ("celltype37")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype37.png){height=200}

[3D visualisation](celltype_RGLs/celltype37.html){target="_blank"}

```{r}
#| echo: false

# MS neurons celltype35-38
annot <- ("celltype38")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype38.png){height=200}

[3D visualisation](celltype_RGLs/celltype38.html){target="_blank"}

#### Chaetal mechanosensory neurons

```{r}
#| echo: false

# chaeMech
annot <- ("celltype71")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype71.png){height=200}

[3D visualisation](celltype_RGLs/celltype71.html){target="_blank"}

#### Other putative mechanosensory neurons in the mechanosensory girdle

```{r}
#| echo: false
#SNantlerPDF
annot <- ("celltype26")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype26.png){height=200}

[3D visualisation](celltype_RGLs/celltype26.html){target="_blank"}

```{r}
#| echo: false
#SNblunt
annot <- ("celltype148")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype148.png){height=200}

[3D visualisation](celltype_RGLs/celltype148.html){target="_blank"}

```{r}
#| echo: false
#SNbronto
annot <- ("celltype168")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype168.png){height=200}

[3D visualisation](celltype_RGLs/celltype168.html){target="_blank"}

```{r}
#| echo: false
#SNFVa
annot <- ("celltype143")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype143.png){height=200}

[3D visualisation](celltype_RGLs/celltype143.html){target="_blank"}

```{r}
#| echo: false
#SNPDF-pyg
annot <- ("celltype115")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype115.png){height=200}

[3D visualisation](celltype_RGLs/celltype115.html){target="_blank"}

```{r}
#| echo: false
#SNpygM
annot <- ("celltype170")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype170.png){height=200}

[3D visualisation](celltype_RGLs/celltype170.html){target="_blank"}

### Nuchal organ chemoreceptors

```{r}
#| echo: false

# PU neurons celltype13-15
annot <- ("celltype13")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype13.png){height=200}

[3D visualisation](celltype_RGLs/celltype13.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype13-15
annot <- ("celltype14")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype14.png){height=200}

[3D visualisation](celltype_RGLs/celltype14.html){target="_blank"}

```{r}
#| echo: false

# PU neurons celltype13-15
annot <- ("celltype15")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype15.png){height=200}

[3D visualisation](celltype_RGLs/celltype15.html){target="_blank"}

### Mushroom body sensory cells

```{r}
#| echo: false
#SNtrpa
annot <- ("celltype190")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype190.png){height=200}

[3D visualisation](celltype_RGLs/celltype190.html){target="_blank"}

```{r}
#| echo: false
#SNtorii
annot <- ("celltype187")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype187.png){height=200}

[3D visualisation](celltype_RGLs/celltype187.html){target="_blank"}

```{r}
#| echo: false
#SNmus
annot <- ("celltype25")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype25.png){height=200}

[3D visualisation](celltype_RGLs/celltype25.html){target="_blank"}

```{r}
#| echo: false
#	SNMB2
annot <- ("celltype32")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype32.png){height=200}

[3D visualisation](celltype_RGLs/celltype32.html){target="_blank"}

```{r}
#| echo: false
#SNlasso
annot <- ("celltype20")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype20.png){height=200}

[3D visualisation](celltype_RGLs/celltype20.html){target="_blank"}

```{r}
#| echo: false
#SNhorn
annot <- ("celltype17")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype17.png){height=200}

[3D visualisation](celltype_RGLs/celltype17.html){target="_blank"}

```{r}
#| echo: false
#SNhook
annot <- ("celltype18")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype18.png){height=200}

[3D visualisation](celltype_RGLs/celltype18.html){target="_blank"}

```{r}
#| echo: false
#SNgolden
annot <- ("celltype16")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype16.png){height=200}

[3D visualisation](celltype_RGLs/celltype16.html){target="_blank"}

```{r}
#| echo: false
#SN-NS27
annot <- ("celltype137")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype137.png){height=200}

[3D visualisation](celltype_RGLs/celltype137.html){target="_blank"}

```{r}
#| echo: false
#SN-NS19
annot <- ("celltype133")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype133.png){height=200}

[3D visualisation](celltype_RGLs/celltype133.html){target="_blank"}

```{r}
#| echo: false
#SN-NS18
annot <- ("celltype138")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype138.png){height=200}

[3D visualisation](celltype_RGLs/celltype138.html){target="_blank"}

```{r}
#| echo: false
#SN-NS17
annot <- ("celltype131")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype131.png){height=200}

[3D visualisation](celltype_RGLs/celltype131.html){target="_blank"}

```{r}
#| echo: false
#SN-NS1
annot <- ("celltype110")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype110.png){height=200}

[3D visualisation](celltype_RGLs/celltype110.html){target="_blank"}

### Apical organ sensory cells

```{r}
#| echo: false
#	SNadNS22
annot <- ("celltype141")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype141.png){height=200}

[3D visualisation](celltype_RGLs/celltype141.html){target="_blank"}

```{r}
#| echo: false
#	SN47Ach
annot <- ("celltype52")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype52.png){height=200}

[3D visualisation](celltype_RGLs/celltype52.html){target="_blank"}

```{r}
#| echo: false
#	SN-YF5cil
annot <- ("celltype132")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype132.png){height=200}

[3D visualisation](celltype_RGLs/celltype132.html){target="_blank"}

```{r}
#| echo: false
#	SN47Ach
annot <- ("celltype52")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype52.png){height=200}

[3D visualisation](celltype_RGLs/celltype52.html){target="_blank"}

```{r}
#| echo: false
#	SN-WLD
annot <- ("celltype48")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype48.png){height=200}

[3D visualisation](celltype_RGLs/celltype48.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS6
annot <- ("celltype135")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype135.png){height=200}

[3D visualisation](celltype_RGLs/celltype135.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS5
annot <- ("celltype130")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype130.png){height=200}

[3D visualisation](celltype_RGLs/celltype130.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS4
annot <- ("celltype112")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype112.png){height=200}

[3D visualisation](celltype_RGLs/celltype112.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS3
annot <- ("celltype111")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype111.png){height=200}

[3D visualisation](celltype_RGLs/celltype111.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS29
annot <- ("celltype136")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype136.png){height=200}

[3D visualisation](celltype_RGLs/celltype136.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS22
annot <- ("celltype129")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype129.png){height=200}

[3D visualisation](celltype_RGLs/celltype129.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS20
annot <- ("celltype134")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype134.png){height=200}

[3D visualisation](celltype_RGLs/celltype134.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS16
annot <- ("celltype139")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype139.png){height=200}

[3D visualisation](celltype_RGLs/celltype139.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS15
annot <- ("celltype113")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype113.png){height=200}

[3D visualisation](celltype_RGLs/celltype113.html){target="_blank"}

```{r}
#| echo: false
#	SN-MIP4
annot <- ("celltype45")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype45.png){height=200}

[3D visualisation](celltype_RGLs/celltype45.html){target="_blank"}

```{r}
#| echo: false
#	SN-MIP1
annot <- ("celltype46")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype46.png){height=200}

[3D visualisation](celltype_RGLs/celltype46.html){target="_blank"}

```{r}
#| echo: false
#	SN-IRP2-FMRF
annot <- ("celltype44")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype44.png){height=200}

[3D visualisation](celltype_RGLs/celltype44.html){target="_blank"}

```{r}
#| echo: false
#	SN-IRP2-burs
annot <- ("celltype43")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype43.png){height=200}

[3D visualisation](celltype_RGLs/celltype43.html){target="_blank"}

```{r}
#| echo: false
#	SN-ASTC
annot <- ("celltype39")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype39.png){height=200}

[3D visualisation](celltype_RGLs/celltype39.html){target="_blank"}

See also @sec-cPRC for the apical organ ciliary photoreceptors.

### Dorsolateral sensory organ sensory cells

```{r}
#| echo: false
#	SN0DLSO1.2-4
annot <- ("celltype28")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype28.png){height=200}

[3D visualisation](celltype_RGLs/celltype28.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO3-PDF
annot <- ("celltype40")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype40.png){height=200}

[3D visualisation](celltype_RGLs/celltype40.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO3
annot <- ("celltype41")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype41.png){height=200}

[3D visualisation](celltype_RGLs/celltype41.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO2
annot <- ("celltype31")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype31.png){height=200}

[3D visualisation](celltype_RGLs/celltype31.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.3
annot <- ("celltype163")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype163.png){height=200}

[3D visualisation](celltype_RGLs/celltype163.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.2-3
annot <- ("celltype29")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype29.png){height=200}

[3D visualisation](celltype_RGLs/celltype29.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.2-1
annot <- ("celltype30")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype30.png){height=200}

[3D visualisation](celltype_RGLs/celltype30.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.1NP
annot <- ("celltype172")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype172.png){height=200}

[3D visualisation](celltype_RGLs/celltype172.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.1
annot <- ("celltype173")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype173.png){height=200}

[3D visualisation](celltype_RGLs/celltype173.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.0
annot <- ("celltype103")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype103.png){height=200}

[3D visualisation](celltype_RGLs/celltype103.html){target="_blank"}

### Other sensory cells (unclear modality)

```{r}
#| echo: false
#SNMIP-vc
annot <- ("celltype24")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype24.png){height=200}

[3D visualisation](celltype_RGLs/celltype24.html){target="_blank"}

```{r}
#| echo: false
#SNPDF-dc
annot <- ("celltype27")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype27.png){height=200}

[3D visualisation](celltype_RGLs/celltype27.html){target="_blank"}

```{r}
#| echo: false
#	SN-DSO
annot <- ("celltype49")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype49.png){height=200}

[3D visualisation](celltype_RGLs/celltype49.html){target="_blank"}

```{r}
#| echo: false
#	SNbicil
annot <- ("celltype50")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype50.png){height=200}

[3D visualisation](celltype_RGLs/celltype50.html){target="_blank"}

```{r}
#| echo: false
#SNasym
annot <- ("celltype51")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype51.png){height=200}

[3D visualisation](celltype_RGLs/celltype51.html){target="_blank"}

```{r}
#| echo: false
#SNaanc
annot <- ("celltype114")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype114.png){height=200}

[3D visualisation](celltype_RGLs/celltype114.html){target="_blank"}

```{r}
#| echo: false
#SNstiff
annot <- ("celltype167")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```

![](snapshots/celltype167.png){height=200}

[3D visualisation](celltype_RGLs/celltype167.html){target="_blank"}

## Interneurons

### Visual system interneurons

```{r}
#| echo: false
#IN1
annot <- ("celltype2")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype2.png){height=200}
[3D visualisation](celltype_RGLs/celltype2.html){target="_blank"}

```{r}
#| echo: false
#INton
annot <- ("celltype3")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype3.png){height=200}
[3D visualisation](celltype_RGLs/celltype3.html){target="_blank"}

```{r}
#| echo: false
#INR1
annot <- ("celltype171")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype171.png){height=200}
[3D visualisation](celltype_RGLs/celltype171.html){target="_blank"}

### Ciliomotor interneurons

```{r}
#| echo: false
#cMNATO
annot <- ("celltype11")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype11.png){height=200}

[3D visualisation](celltype_RGLs/celltype11.html){target="_blank"}

```{r}
#| echo: false
#cMNdc
annot <- ("celltype12")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype12.png){height=200}

[3D visualisation](celltype_RGLs/celltype12.html){target="_blank"}

```{r}
#| echo: false
#cMNPDF-vcl1
annot <- ("celltype10")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype10.png){height=200}

[3D visualisation](celltype_RGLs/celltype10.html){target="_blank"}

### Apical organ interneurons

```{r}
#| echo: false
#INNOS
annot <- ("celltype7")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype7.png){height=200}
[3D visualisation](celltype_RGLs/celltype7.html){target="_blank"}

```{r}
#| echo: false
#INRGWa
annot <- ("celltype6")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype6.png){height=200}
[3D visualisation](celltype_RGLs/celltype6.html){target="_blank"}

### Central brain interneurons

```{r}
#| echo: false
#INexsn
annot <- ("celltype188")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype188.png){height=200}
[3D visualisation](celltype_RGLs/celltype188.html){target="_blank"}

```{r}
#| echo: false
#INface
annot <- ("celltype193")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype193.png){height=200}
[3D visualisation](celltype_RGLs/celltype193.html){target="_blank"}

```{r}
#| echo: false
#INmidL
annot <- ("celltype118")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype118.png){height=200}
[3D visualisation](celltype_RGLs/celltype118.html){target="_blank"}

```{r}
#| echo: false
#INmus
annot <- ("celltype174")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype174.png){height=200}
[3D visualisation](celltype_RGLs/celltype174.html){target="_blank"}

```{r}
#| echo: false
#INpara
annot <- ("celltype196")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype196.png){height=200}
[3D visualisation](celltype_RGLs/celltype196.html){target="_blank"}

```{r}
#| echo: false
#INsn
annot <- ("celltype57")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype57.png){height=200}
[3D visualisation](celltype_RGLs/celltype57.html){target="_blank"}

```{r}
#| echo: false
#INsqNSasym
annot <- ("celltype179")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype179.png){height=200}
[3D visualisation](celltype_RGLs/celltype179.html){target="_blank"}

### Central brain decussating interneurons

```{r}
#| echo: false
#INarc1
annot <- ("celltype55")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype55.png){height=200}
[3D visualisation](celltype_RGLs/celltype55.html){target="_blank"}

```{r}
#| echo: false
#INarc2
annot <- ("celltype56")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")

```

![](snapshots/celltype56.png){height=200}
[3D visualisation](celltype_RGLs/celltype56.html){target="_blank"}

>>>>

---
format:
  html:
    smooth-scroll: true
    theme: [default, custom_index.scss]

---

## Whole-body connectome of a segmented annelid larva

#### Interactive visualisations and resources of the *Platynereis dumerilii* three-day-old larvae whole-body connectome based on the [connectome paper](https://elifesciences.org/reviewed-preprints/97964v1){.external target="_blank"}.

#### by the Jékely lab, [Centre for Organismal Studies](https://www.cos.uni-heidelberg.de/en/research-groups/gaspar-jekely){.external target="_blank"}, Heidelberg University

<br>

::: columns
::: {.column width="31%"}

![](Platynereis_SEM_3d_2.png)
:::
::: {.column width="4%"}
:::
::: {.column width="65%"}

![](network_with_IO_layout.png)
:::
:::

<br>

[Morphological rendering of brain ganglia](celltype_compendium/celltype_RGLs/brain_ganglia.html){.external target="_blank"} of the three-day-old *Platynereis dumerilii* larva.
<br>

[Morphological rendering of the mushroom bodies](celltype_compendium/celltype_RGLs/mushroom_bodies.html){.external target="_blank"} of the three-day-old *Platynereis dumerilii* larva.
<br>

[Morphological rendering of the mechanosensory girdle](celltype_compendium/celltype_RGLs/mechanosensory_girdle.html){.external target="_blank"} of the three-day-old *Platynereis dumerilii* larva.
<br>

[Cell type compendium](celltype_compendium/index.html){.external target="_blank"} of the three-day-old *Platynereis dumerilii* larva.
<br>

[Interactive visualisation of the connectome graph](Full_connectome_modules_with_names.html){.external target="_blank"} of the three-day-old *Platynereis dumerilii* larva, containing all cells in the whole-body connectome. Nodes represent individual neurons or effector cells. Directed edges (arrows) represent synaptic connections from the presynaptic neuron to the postsynaptic cell. Nodes are coloured by connectome module.
<br>

[Interactive visualisation of the cell-type-level connectome graph](Figure4_celltype_network.html){.external target="_blank"} of the three-day-old *Platynereis dumerilii* larva. Nodes represent cell types (cells grouped into one node by cell type).
<br>

[Interactive visualisation of the cell-type-level connectome graph](network_with_transmitters.html){.external target="_blank"}, same graph as before, but the nodes are coloured by transmitter phenotype.
<br>

[Interactive visualisation of the cell-type-level connectome graph](network_with_IO_layout.html){.external target="_blank"}, same graph as before, but the nodes are arranged based on the ratio of incoming to outgoing synapses.
